### 2016-06-29 Projects/DelCo_2012/Report/DelCo_2012.tex
update report, crop two figures, CAFS

To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAFS Test 1 as a result of the hallway (first) and room (second) suppression actions.

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:fs_1_1}
\end{figure}

@@

@@

@@

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:app_fs_1}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:app_fs_2}
\end{figure}

>>>>

To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAFS Test 1 as a result of the hallway (first) and room (second) suppression actions. Fig.~\ref{fig:fs_1_2} shows the same impacts as Fig.~\ref{fig:fs_1_1}, except that the tests used water.

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:fs_1_1}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
	\label{fig:fs_1_2}
\end{figure}

@@

\section{Spray density figures for burn building tests}

@@

\section{Spray density figures for experimental structure tests}

@@

\begin{figure}[ht!]
\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_1}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_2}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 2 with a 7/8'' 
Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_3}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 2 with a 7/8'' 
Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_4}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 3 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_5}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 3 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_6}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 4 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_7}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 4 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_8}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 5 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_11}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 5 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_12}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 6 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_13}
\end{figure}

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 6 with a 30$^{\circ}$ Fog nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
\label{fig:app_fs_14}
\end{figure}
